---
title: "British Columbia Rainfall map"
output: 
  flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
library(flexdashboard)

library(tidyr)
library(dplyr)
library(magrittr)

library(ggplot2)

library(leaflet)
library(leaflet.extras)

library(raster)
library(sf)
library(terra)
```

```{r data loading, include=FALSE}
# ECCC Data
info_stations <- read.csv("dat/info_stations.csv", header = TRUE)
info_stations %<>% dplyr::select(Name, ID, Lat, Lon, Elevation)

info_stations %<>% mutate(Label = paste("<b>", Name, 
                                 "</b><br>ID : ", ID, 
                                 "<br>Latitude : ", Lat, 
                                 "<br>Longitude : ", Lon, 
                                 "<br>Elevation : ", Elevation, " m"))

coords <- read.csv("dat/results/gev/gev_24h-clean.csv", header = TRUE)

focus = c("VANCOUVER UBC", "PLEASANT CAMP", "GERMANSEN LANDING", "DUNCAN LAKE DAM")

coords %<>% mutate(Label = paste("<b>", Name, 
                                 "</b><br>ID : ", ID, 
                                 "<br>Latitude : ", Lat, 
                                 "<br>Longitude : ", Lon, 
                                 "<br>Elevation : ", Elevation, " m",
                                 "<br>μ : ", μ,
                                 "<br>ϕ : ", ϕ,
                                 "<br>ξ : ", ξ,
                                 "<br>q20 : ", q20))
coords %<>% mutate(foc = Name %in% focus)


# Gridded covariates
model = "P"

caspar_mean <- read.csv(paste("dat/CaSPAr/BC_meanPcp_", model, ".csv", sep=""), header = TRUE)
caspar_mean$GridCell <- 1:nrow(caspar_mean)
caspar_gev <- read.csv(paste("dat/CaSPAr/BC_GEV_", model, ".csv", sep=""), header = TRUE)

elevation <- read.csv("dat/Elevation/grid-open_meteo.csv", header = TRUE)
elevation$GridCell <- 1:nrow(elevation)


grid <- caspar_mean %>% 
  inner_join(caspar_gev, by = "GridCell") %>%
  inner_join(elevation, by = "GridCell") %>%
  dplyr::select(Lat.x, Lon.x, GridCell, q, Pcp, Elevation)

colnames(grid) <- c("Lat", "Lon", "GridCell", "q", "Pcp", "Elevation")

# results from MCMC best model
results <- read.csv(paste("dat/results/grid/grid-tridim_opti_", model, ".csv", sep=""),header = TRUE)
```



Presentation
==========================

Column {data-width=800}
---------------------------

### Map

```{r complete.map}

rad = 6.5
elevation.pal <- colorNumeric(
  palette = "YlOrRd",
  domain = info_stations$Elevation)

leaflet(data = info_stations) %>%
  addTiles() %>%
  addCircleMarkers(lng = ~Lon,
              lat = ~Lat,
             popup = ~Label,
             label = ~Name,
             fillOpacity = 0.8,
             radius = rad,
             fillColor = ~elevation.pal(Elevation),
             stroke = FALSE) %>%
  addLegend(position = "topright",
            pal = elevation.pal,
            values = ~Elevation,
            title = "Altitude in m",
            labFormat = labelFormat(suffix = " m"),
            opacity = 1) %>%
  addResetMapButton()


```



Column {data-width=200}
----------------------------

### Project Presentation


ECCC Stations' map
==========================

Column {data-width=800}
---------------------------

### Map

```{r ECCC.map}
rad = 6.5

elevation.pal <- colorNumeric(
  palette = "YlOrRd",
  domain = coords$Elevation)

location.pal <- colorNumeric(
  palette = "YlOrRd",
  domain = coords$μ)

scale.pal <- colorNumeric(
  palette = "YlOrRd",
  domain = coords$ϕ)

shape.pal <- colorNumeric(
  palette = c("blue", "yellow", "red"),
  domain = coords$ξ)

quantile.pal <- colorNumeric(
  palette = "YlOrRd",
  domain = coords$q20)

leaflet(data = coords) %>%
  addTiles() %>%
  addCircleMarkers(lng = ~Lon,
              lat = ~Lat,
             popup = ~Label,
             label = ~Name,
             fillOpacity = 0.8,
             radius = rad,
             fillColor = ~elevation.pal(Elevation),
             stroke = FALSE,
             group = "Elevation") %>%
  addLegend(position = "topright",
            pal = elevation.pal,
            values = ~Elevation,
            title = "Altitude in m",
            labFormat = labelFormat(suffix = " m"),
            opacity = 1,
            group = "Elevation",
            layerId = "Elevation") %>%
  addCircleMarkers(lng = ~Lon,
              lat = ~Lat,
             popup = ~Label,
             label = ~Name,
             stroke = FALSE,
             fillOpacity = 0.8,
             radius = rad,
             color = ~location.pal(μ),
             group = "Location") %>%
  addLegend(position = "topright",
            pal = location.pal,
            values = ~μ,
            title = "Location parameter μ",
            opacity = 1,
            group = "Location",
            layerId = "Location") %>%
  addCircleMarkers(lng = ~Lon,
              lat = ~Lat,
             popup = ~Label,
             label = ~Name,
             stroke = FALSE,
             fillOpacity = 0.8,
             radius = rad,
             color = ~scale.pal(ϕ),
             group = "Scale") %>%
  addLegend(position = "topright",
            pal = scale.pal,
            values = ~ϕ,
            title = "Scale parameter ϕ",
            opacity = 1,
            group = "Scale",
            layerId = "Scale") %>%
  addCircleMarkers(lng = ~Lon,
              lat = ~Lat,
             popup = ~Label,
             label = ~Name,
             stroke = FALSE,
             fillOpacity = 0.8,
             radius = rad,
             color = ~shape.pal(ξ),
             group = "Shape") %>%
  addLegend(position = "topright",
            pal = shape.pal,
            values = ~ξ,
            title = "Shape parameter ξ",
            opacity = 1,
            group = "Shape",
            layerId = "Shape") %>%
  addCircleMarkers(lng = ~Lon,
              lat = ~Lat,
              popup = ~Label,
              label = ~Name,
             fillOpacity = 0,
             radius = rad,
             stroke = ~foc,
             color = "black", 
             group = "Focus") %>%
  addLayersControl(
    baseGroups = c("Elevation", "Location", "Scale", "Shape"),
    overlayGroups = c("Focus"),
    options = layersControlOptions(collapsed = FALSE),
    position = "bottomleft") %>%
  addResetMapButton() %>%
  htmlwidgets::onRender("
    function() { 
      var map = this;
      var legends = map.controls._controlsById;
      function addActualLegend() {
         var sel = $('.leaflet-control-layers-base').find('input[type=\"radio\"]:checked').siblings('span').text().trim();
         $.each(map.controls._controlsById, (nm) => map.removeControl(map.controls.get(nm)));
         map.addControl(legends[sel]);
      }
      $('.leaflet-control-layers-base').on('click', addActualLegend);
      addActualLegend();
   }")
```


Column {data-width=200}
----------------------------

### ECCC Data explanation

This map showcases the data collected from 120 ECCC's stations all around British Columbia. Among the starting 134 stations, 14 of them were scrapped out from this study, as we needed one station for each grid cell at most, and some of the stations had aberrant results (the most being the oceant front side station at Moresby Island).


The "focus" overlay showcases the four stations that were chosen arbitrairly during the study to provide the trace from MCMC.


Covariates
==========================

Column {data-width=800}
----------------------------

### Map

```{r Covariates.map}
rad = 2
op = 0.3


# -- RASTERS CREATION

#generic base raster
e <- extent(as.matrix(dplyr::select(grid, Lon, Lat))[, 1:2])
r <- raster(e, ncol = 150, nrow = 200) #a preciser pour la taille de la grille

# GEV quantile

quantile.matrix <- grid %>% 
  dplyr::select(Lat, Lon, q) %>%
  as.matrix()

quantile.raster <- raster::rasterize(quantile.matrix[, 2:1], r, quantile.matrix[,3], fun=mean)
raster::crs(quantile.raster) <- sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

quantile.pal <- colorNumeric(
  palette = "YlOrRd",
  domain = raster::values(quantile.raster),
  na.color = "transparent")

# Mean precipitation
pcp.matrix <- grid %>% 
  dplyr::select(Lat, Lon, Pcp) %>%
  as.matrix()

pcp.raster <- raster::rasterize(pcp.matrix[, 2:1], r, pcp.matrix[,3], fun=mean)
raster::crs(pcp.raster) <- sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

pcp.pal <- colorNumeric(
  palette = "YlOrRd",
  domain = raster::values(pcp.raster),
  na.color = "transparent")

# Elevation
elevation.matrix <- grid %>% 
  dplyr::select(Lat, Lon, Elevation) %>%
  as.matrix()

elevation.raster <- raster::rasterize(elevation.matrix[, 2:1], r, elevation.matrix[,3], fun=mean)
raster::crs(elevation.raster) <- sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

elevation.pal <- colorNumeric(
  palette = "YlOrRd",
  domain = raster::values(elevation.raster),
  na.color = "transparent")



m <- leaflet() %>%
  addTiles() %>%
  addRasterImage(quantile.raster,
                 colors = quantile.pal,
                 opacity = 0.8,
                 group = "Quantile") %>%
  addLegend(position = "topright",
            pal = quantile.pal, 
            values = raster::values(quantile.raster),
            title = "20-years return level in mm/h",
            opacity = 1,
            group = "Quantile",
            layerId = "Quantile") %>%
  addRasterImage(pcp.raster,
                 colors = pcp.pal,
                 opacity = 0.8,
                 group = "Mean precipitation") %>%
  addLegend(position = "topright",
            pal = pcp.pal, 
            values = raster::values(pcp.raster),
            title = "Annual mean precipitation in mm/h",
            opacity = 1,
            group = "Mean precipitation",
            layerId = "Mean precipitation") %>%
  addRasterImage(elevation.raster,
                 colors = elevation.pal,
                 opacity = 0.8,
                 group = "Elevation") %>%
  addLegend(position = "topright",
            pal = elevation.pal, 
            values = raster::values(elevation.raster),
            title = "Elevation in m",
            opacity = 1,
            group = "Elevation",
            layerId = "Elevation") %>%
  addLayersControl(
    baseGroups = c("Quantile", "Mean precipitation", "Elevation"),
    options = layersControlOptions(collapsed = FALSE),
    position = "bottomleft") %>%
  addResetMapButton() %>%
  htmlwidgets::onRender("
    function() { 
      var map = this;
      var legends = map.controls._controlsById;
      function addActualLegend() {
         var sel = $('.leaflet-control-layers-base').find('input[type=\"radio\"]:checked').siblings('span').text().trim();
         $.each(map.controls._controlsById, (nm) => map.removeControl(map.controls.get(nm)));
         map.addControl(legends[sel]);
      }
      $('.leaflet-control-layers-base').on('click', addActualLegend);
      addActualLegend();
   }")
m

```

Column {data-width=200}
----------------------------

### CaSPAr models summary

Blablabla







